Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-09-22 R0V0.tex
Small changes on the outline paragraph
Correct from LPV systems and LTI systems

@@

\usepackage[natbib=true,backend=bibtex,style=ieee,
firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
\addbibresource{../../../../Library.bib}
\AtBeginBibliography{\small}

@@

Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear parameter-varying systems (LPVS) (see \cite[Ch. 2 and 3]{Briat2015} for more information on LPVS).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 																			   %
% Git Branch: Master	 													   %
% 																			   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage[natbib=true,backend=biber,style=ieee,
firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
\addbibresource[location=remote]{https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1} 
\AtBeginBibliography{\small}

@@

Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear time-varying systems (LTIS) (see \cite{Hespanha:2009} for more information on LTIS).
